---
title: "homework_3"
author: "Brian Hernandez"
date: "June 20, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
setwd("C:/Users/Brian Hernandez/Projects/ds3/coursework/week2")
oj <- read.csv("oj.csv")

```

## Demographics vs Demand

```{r dvd}

lm(formula = logmove ~ log(price)*brand*feat, data = oj) %>% 
  summary()

lm(formula = logmove ~ log(price)*brand*feat + AGE60 + EDUC + ETHNIC + INCOME + HHLARGE + WORKWOM + HVAL150, data = oj) %>% 
  summary()

```
All of the features are statistically significant.

The R-squared increases by .05

## Household income and Education with respect to Quantity

``` {r hval_educ}

summary(oj$HVAL150)

regression_demo <- lm(formula = logmove ~ log(price)*brand*feat + AGE60 + EDUC + ETHNIC + INCOME + HHLARGE + WORKWOM + HVAL150, data = oj)
exp(coef(regression_demo)["HVAL150"] * (summary(oj$HVAL150)["3rd Qu."] - summary(oj$HVAL150)["Median"]))
exp(coef(regression_demo)["EDUC"] * (summary(oj$EDUC)["3rd Qu."] - summary(oj$EDUC)["Median"]))

```

## Household income and Education with respect to Quantity including Interaction

``` {r hval_educ_interaction}

regression_demo_interaction <-lm(formula = logmove ~ log(price)*brand*feat + AGE60 + ETHNIC + INCOME + HHLARGE + WORKWOM + log(price)*HVAL150 + log(price)*EDUC, data = oj)
coef(regression_demo_interaction)["log(price):HVAL150"]
coef(regression_demo_interaction)["log(price):EDUC"]
exp(coef(regression_demo_interaction)["log(price):HVAL150"] * (summary(oj$HVAL150)["3rd Qu."] - summary(oj$HVAL150)["Median"]))
exp(coef(regression_demo_interaction)["log(price):EDUC"] * (summary(oj$EDUC)["3rd Qu."] - summary(oj$EDUC)["Median"]))

```

These results are in line with intuition since the sensitivity to price is reduced when there is a greater percentage of higher income households and the sensitivity to price is increased when there is a greater level of education.

The coefficient for HVAL150 for this regression is `r coef(regression_demo_interaction)["log(price):HVAL150"]`
The coefficient for EDUC for this regression is `r coef(regression_demo_interaction)["log(price):EDUC"]`

The change in elasticity with respect to HVAL150 and price is `r exp(coef(regression_demo_interaction)["log(price):HVAL150"] * (summary(oj$HVAL150)["3rd Qu."] - summary(oj$HVAL150)["Median"]))`
The change in elasticity with respect to HVAL150 and price is `r exp(coef(regression_demo_interaction)["log(price):EDUC"] * (summary(oj$EDUC)["3rd Qu."] - summary(oj$EDUC)["Median"]))`

*Based on these results in can be said that the level of education in a neighborhood is more important to price sensitivity than the household income*

``` {r five_fold_cross_validation}

set.seed(21)
random_oj <- oj %>%
  sample_n(nrow(oj))
random_oj$id <- seq(1, nrow(oj))
random_oj$assignment <- random_oj$id %% 5 + 1
MSE <- c(1:5)

for(i in 1:5){
  test_set_i <- random_oj %>%
    filter(assignment == i)
  train_set_i <- anti_join(random_oj, test_set_i)
  regression_demo <- lm(formula = logmove ~ log(price)*brand*feat + AGE60 + EDUC + ETHNIC + INCOME + HHLARGE + WORKWOM + HVAL150, data = train_set_i)
  
}


```