---
title: "lee_rd_replication"
author: "Brian Hernandez"
date: "June 29, 2018"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rdd)

lee <- read.csv('lee_rd_replication.csv')

```

##DWinNxt ~ DemWin

```{r simple_regression}

simple_regression <- lm(formula = DWinNxt ~ DemWin, data = lee)
summary(dwin_regression)

```

This regression seems to give a biased estimate because we are not controlling for other variables.

##Potential Controls
**ForgnPct**: Confounding
**GovWkPct**: Unrelated
**BlackPct**: Confounding
**UrbanPct**: Confounding
**DWinPrv**: Confounding
**YearElec**: Unrelated
**CDNum**: Confounding as factor

```{r potential_controls}

controlled_regression <- lm(formula = DWinNxt ~ DemWin + ForgnPct + BlackPct + UrbanPct + DWinPrv, data = lee)
summary(controlled_regression)

```

The coefficient of DemWin has decreased as a result of controlling for these variables.

##Bad Controls
Examples of bad controls for this regression would be DWinNxt, CpnFun, PoliChge, MajPty

##DifDPct as a Forcing Variable
```{r dif_d_pct}

threshold <- 0
window_size <- 10
poly_degree <- 3

RD_data <- lee %>% 
  filter(DifDPct < threshold + window_size & DifDPct > threshold - window_size) %>%
  mutate(is_above = ifelse(DifDPct > threshold, 1, 0)) %>%
  mutate(is_below = (is_above + 1) %% 2)


forced_regression <- lm(formula = DWinNxt ~ DemWin + ForgnPct + BlackPct + UrbanPct + DWinPrv + DemWin*poly(DifDPct, 3, raw=TRUE), data = RD_data)
summary(forced_regression)
RD_data$predictions <- predict(forced_regression, RD_data)

RD_data %>%
  ggplot(aes(x = DifDPct, y = predictions)) +
  geom_point() +
  geom_smooth(aes(color=as.factor(DemWin)))

```

The coefficients when compared to (b) and (c) are a lot smaller. This supports the hypothesis that the actual incumbency effect is smaller than our simple regression.

##Using rdd Library
```{r rdd_regression}

rdd_regression <- RDestimate(formula = DWinNxt ~ DifDPct, data=lee)
summary(rdd_regression)
plot(rdd_regression)

```